%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Job experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full stack developer and owner}
    {Enfok shop}
    {Guadalajara, México}
    {2014 - present}
    {
      \begin{cvitems}
        \item {Deploy and development of an ecommerce project using the following stack: Saleor (Django), Nginx, Celery, Bootstrap, Jquery, all in a Debian environment hosted on a Digital Ocean Droplet.}
        \item {Add a cash payment gateway, compatible with proof of payment receipts, PDF generator using weasyprint.}
        \item {Implement a Mercado Pago gateway through the creation of a library that integrates the Mercado Pago API and the django-payments library.}
        \item {Adquisition of +1000 new suscriptors in less than a week, without using ads, creating an affiliate newsletter systems for email marketing.}
        \item {Improved funnel conversion rate metrics, after a successful facebook pixel synchronization.}
        %\item {Integrar sistemas de: calificación de productos, estimador de tiempos de entrega, historial de consultas, notificaciones, opiniones, manejo de códigos postales y colonias}
        %\item {Facilitar el mantenimiento de la Facebook store tras la automatización de la exportación de los productos en la base de datos a un archivo csv compatible}
        \item {Completely automate the product publication processes in facebook groups using Selenium, without using the official API.}
        \item {Reduce the individual image creation time from hours to a few seconds with an image batch creation script based on Python Pillow, Image Magick and Bash.}
        \item {Improve the web performance metrics in Lighthouse by query optimization, defering the scripts load and refactoring code. Results 93, 98, 93 and 100 (Performance, Accessibility, Best Practices, SEO) for mobile devices and 98, 100, 93 y 100 for desktop.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web development blogger}
    {Coffee Bytes}
    {Guadalajara, México}
    {March 2019 - present}
    {
      \begin{cvitems}
        \item {I write frequently, mostly about Go, Django, GNU/Linux and React.}
        \item {Project manteined on a Digital Ocean Droplet, Ubuntu, using a headless WordPress as the backend and Frontity as the frontend.}
      \end{cvitems}
    }

\end{cventries}

